---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MacaqueNet data processing pipeline

<!-- badges: start -->

<!-- badges: end -->

This repository contains the infrastructure to import, process, clean and check the data that end up in the MacaqueNet database. 
It also includes a set of made-up data sets to illustrate the workflow.

In order to recreate the workflow we use(d) during the building of the database you need to clone this repository, i.e. we work with a local version of all the files in this repository. 
Simply *installing* the package won't suffice. 
We highly recommend to use RStudio in combination with the `devtools` package.
[Below](#setup) we provide a short description for setting up your system.
In brief: download and unpack the zipped version of this repository. 
Then create an RStudio project with the content of this folder.
If you are familiar with `git` and `GitHub` you can also directly create a local copy of the repository via RStudio's `New project...` menu option where we need to provide the URL to the GitHub repository.

The general workflow with this setup is the following for adding a new data set:

- add new raw data to the `data-raw/original_data_files/` 

- fill the file `inst/extdata/_datakey.csv` with necessary information

- edit the `R/read_subject_data.R` function

- edit the `R/read_interaction_data.R` and `R/cleaning.R` functions

- run tests on new data

- build all data files (create standardized csv files of all data files) into the `inst/extdata` folder

- run tests across all data

- install the package





```{r, eval=FALSE}
library(macaquenetpipeline)
key <- get_key(ready_to_deploy_only = TRUE)
build_all(key = key, ready_to_deploy_only = TRUE, silent = TRUE, scramble = FALSE)
match_subjects_interactions(key = key)
export_project_data(output_folder = tempdir())
```



# setup

We recommend using a recent version of RStudio.
Within RStudio, we also recommend using the *project* feature.
The main reason for using this setup is that it keeps track of working directories and also allows for an easy integration of version control via `git` and `GitHub`.


```{r, eval=FALSE}
devtools::has_devel()
```

If this returns `Your system is ready to build packages!`, you are good to go.

